Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-16 grove-paper.tex
Finish renumbering vertexes and edges in figures

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "$\texttt{+}_{34}$" [> "L$_{33}$"'],
    "$\texttt{*}_{36}$" [> "R$_{35}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "$\texttt{+}_{34}$" [> "R$_{37}$"] -> {
     "$\texttt{*}_{36}$" [> "L$_{39}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "$\texttt{*}_{36}$" [> "R$_{41}$"] -> {
     "$\texttt{+}_{34}$" [> "L$_{43}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    v1/"$\texttt{+}_{34}$" [> "R$_{37}$"],
    v2/"$\texttt{*}_{36}$" [> "R$_{41}$"]
   }
  }
 }
};
\path[edge style,->] (v1) to ["L$_{39}$",out=-45,in=-135] (v2);
\path[edge style,->] (v2) to ["L$_{43}$",out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "$\texttt{*}_{36}$" [> "R$_{41}$"]
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "$\texttt{*}_{36}$" [> "R$_{45}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "$\texttt{*}_{36}$" [> "R$_{37}$"] -> {
    "\vSimpleTimes" [> "L$_{47}$"'],
    {}
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-1cm,-3cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 1cm,-3cm) graph[graph style] { times/"$\texttt{*}_{32}$" };
\path[edge style,->] (times) to ["L$_{43}$"anchor=south,out=-135,in=-45] (plus);
\path[edge style,->] (plus) to ["R$_{41}$"anchor=north,out=45,in=135] (times);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Disconnection}
\label{fig:Disconnection}
\end{figure*}

>>>>

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\newedge{MultiCyclePlus}{L}
\newvertex{MultiCyclePlus}{+}
\newedge{MultiCycleTimes}{R}
\newvertex{MultiCycleTimes}{*}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vMultiCyclePlus" [> "\eMultiCyclePlus"'],
    "\vMultiCycleTimes" [> "\eMultiCycleTimes"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\newedge{MultiCycleAlicePlus}{R}
\newedge{MultiCycleAliceTimes}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "\vMultiCyclePlus" [> "\eMultiCycleAlicePlus"] -> {
     "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\newedge{MultiCycleBobTimes}{R}
\newedge{MultiCycleBobPlus}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    "\vMultiCycleTimes" [> "\eMultiCycleBobTimes"] -> {
     "\vMultiCyclePlus" [> "\eMultiCycleBobPlus"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
   },
   {
    v1/"\vMultiCyclePlus" [> "\eMultiCycleAlicePlus"],
    v2/"\vMultiCycleTimes" [> "\eMultiCycleBobTimes"]
   }
  }
 }
};
\path[edge style,->] (v1) to ["\eMultiCycleAliceTimes",out=-45,in=-135] (v2);
\path[edge style,->] (v2) to ["\eMultiCycleBobPlus",out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vMultiCycleTimes" [> "\eMultiCycleBobTimes"]
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\newedge{DisconnectionAlice}{R}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vMultiCycleTimes" [> "\eDisconnectionAlice"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\newedge{DisconnectionBob}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vMultiCycleTimes" [> "\eMultiCycleAlicePlus"] -> {
    "\vSimpleTimes" [> "\eDisconnectionBob"'],
    {}
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-1cm,-3cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 1cm,-3cm) graph[graph style] { times/"\vMultiCycleTimes" };
\path[edge style,->] (times) to ["\eMultiCycleBobPlus"anchor=south,out=-135,in=-45] (plus);
\path[edge style,->] (plus) to ["\eMultiCycleBobTimes"anchor=north,out=45,in=135] (times);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Disconnection}
\label{fig:Disconnection}
\end{figure*}
